Using Genetic Algorithms to Optimize the Analog Method for Precipitation Downscaling in the Swiss Alps

### 2016-11-07 AtmoSwing - GMD/template.tex
Updating affiliations.

\Author[1,2]{Pascal}{Horton}
\Author[1]{Michel}{Jaboyedoff}
\Author[3]{Charles}{Obled}

\affil[1]{University of Lausanne, Lausanne, Switzerland}
\affil[2]{Terranum, Lausanne, Switzerland}
\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

>>>>

\Author[1,2,3]{Pascal}{Horton}
\Author[1]{Michel}{Jaboyedoff}
\Author[4]{Charles}{Obled}

\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
\affil[3]{Terranum SARL, Bussigny, Switzerland}
\affil[4]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

### 2016-11-07 Genetic algorithms - MWR/template.tex
Updating affiliations.

\affiliation{University of Lausanne, Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}

>>>>

\affiliation{Institute of Earth Sciences, University of Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Switzerland}

### 2016-11-07 Optimization case study - JoH/elsarticle-template.tex
Updating affiliations.

%% Group authors per affiliation:
\author[unil,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{pascal.horton@alumnil.unil.ch}

@@

\address[unil]{University of Lausanne, Lausanne, Switzerland}
\address[terranum]{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland}
\address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

>>>>

%% Group authors per affiliation:
\author[unil,unibe,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{pascal.horton@alumnil.unil.ch}

@@

\address[unil]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
\address[unibe]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
\address[terranum]{Terranum SARL, Bussigny, Switzerland}
\address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
